True versus apparent shapes of bow shocks

### 2018-03-06 papers/Papers1234/sec-conclusions.tex
Start discussing shape of M42 arcs

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/M17-composite}
  \caption[]{Procedure for tracing the contact discontinuity from the
    \citet{Meyer:2017a} simulations.  The density maps from
    \citeauthor{Meyer:2017a}'s Fig.~3 are converted to FITS format and
    displayed using the software \textsc{SAOImage DS9}.  The density
    contour at \SI{0.4}{cm^{-3}} is displayed (shown in green in the
    figure) and this is traced by hand by placing ``point regions'' on
    the image (shown by black ``x'' shapes in the figure).  The zoom
    facility of the software allows the points to be placed with any
    required accuracy.  The points are saved to a file in the DS9
    region file format, which is then read by Python programs for
    further processing.  For example, the yellow boxes show circle
    fits and determination of the parameters \(R_0\), \(R_c\), and
    \(R_{90}\).  In this example, only the points shown in orange
    (within \ang{60} of axis) are used in the fits.}
  \label{fig:meyer-trace}
\end{figure}

@@

We consider three different tracings of the bow shape (see
Fig.~\ref{fig:000-400-fit}): the peak of the emission arc (``ridge''),
and its inner and outer edges.  In all three cases, we placed by eye
the points that define the bow, using SAOImage~DS9 in a similar
fashion to in Figure~\ref{fig:meyer-trace}, and guided by the image
contours.\footnote{%
  In the case of the ``ridge'' method at least, it is possible to
  automate this step, which we will discuss in detail in a following
  paper. } %

@@

It can be seen from Table~\ref{tab:m42-fit} that the uncertainty in
the fitted parameters is dominated by the variations between the
different traced shapes.  For example, the one-sigma relative
variation of planitude \(\Pi'\) is \(< 10\%\) within the individual
tracings, but \(\approx 20\%\) between tracings.  For the mean alatude
\(\langle\Lambda'\rangle\), the variation within individual tracings is extremely
small\footnote{%
  This is because the only way that variation in the circle fit
  parameters affect the alatudes is through the axis orientation
  vector, and changing the orientation induces roughly opposite
  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which cancel out in \(\langle\Lambda'\rangle\).
} %
at \(\approx 1\%\), but is \(\approx 10\%\) between tracings.  The alatude
asymmetry, \(\Delta\Lambda'\), is best interpreted as a difference between the
symmetry axis of the apex region and the symmetry axis of the wings.
In relative terms, this is \(0\)--\(20\%\), but with large systematic
variations between tracings (for instance, in both objects it is very
small for the outer arcs).

It could be argued that much of the between-tracing variations in
\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences in the shape of the
inner and outer boundaries of the emission arc.  Although this may be
true, in the absence of a robust theory as to exactly what feature of
the observed images constitutes \emph{the} bow shock, such variations
nevertheless serve to limit the precision with which the bow shock
shape can be measured.  We therefore conclude that conservative
estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\) precision for
\(\Lambda'\) are appropriate when analyzing observations of a similar
quality to those presented in Figure~\ref{fig:000-400-fit}.

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/M17-composite}
  \caption[]{Procedure for tracing the contact discontinuity from the
    \citet{Meyer:2017a} simulations.  The density maps from
    \citeauthor{Meyer:2017a}'s Fig.~3 are converted to FITS format and
    displayed using the software SAOImage~DS9 \citep{Joye:2003a}.  The
    density contour at \SI{0.4}{cm^{-3}} is displayed (shown in green
    in the figure) and this is traced by hand by placing ``point
    regions'' on the image (shown by black ``x'' shapes in the
    figure).  The zoom facility of the software allows the points to
    be placed with any required accuracy.  The points are saved to a
    file in the DS9 region file format, which is then read by Python
    programs for further processing.  For example, the yellow boxes
    show circle fits and determination of the parameters \(R_0\),
    \(R_c\), and \(R_{90}\).  In this example, only the points shown
    in orange (within \ang{60} of axis) are used in the fits.}
  \label{fig:meyer-trace}
\end{figure}

@@

We consider three different tracings of the bow shape (see
Fig.~\ref{fig:000-400-fit}): the peak of the emission arc (``ridge''),
and its inner and outer edges.  In all three cases, we placed by eye
the points that define the bow, using SAOImage~DS9 \citep{Joye:2003a}
in a similar fashion to in Figure~\ref{fig:meyer-trace}, and guided by
the image contours.\footnote{%
  In the case of the ``ridge'' method at least, it is possible to
  automate this step, which we will discuss in detail in a following
  paper. } %

@@

It can be seen from Table~\ref{tab:m42-fit} that the uncertainty in
the fitted parameters is dominated by the variations between the
different traced shapes.  For example, the one-sigma relative
variation of planitude, \(\Pi'\), is \(< 10\%\) within the individual
tracings, but \(\approx 20\%\) between tracings.  For the mean alatude,
\(\langle\Lambda'\rangle\), the variation within individual tracings is extremely
small\footnote{%
  This is because the only way that variation in the circle fit
  parameters affect the alatudes is through the axis orientation
  vector, and changing the orientation induces roughly opposite
  effects on \(\Lambda_+'\) and \(\Lambda_-'\), which approximately cancel out in
  \(\langle\Lambda'\rangle\).  } %
at \(\approx 1\%\), but is \(\approx 10\%\) between tracings.  The alatude
asymmetry, \(\Delta\Lambda'\), is best interpreted as a difference between the
symmetry axis of the apex region and the symmetry axis of the wings.
In relative terms, this is \(0\)--\(20\%\), but with large systematic
variations between tracings (for instance, in both objects it is very
small for the outer arcs).

It could be argued that much of the between-tracing variations in
\(\Pi'\) and \(\langle\Lambda'\rangle\) are due to real differences in the shape of the
inner and outer boundaries of the emission arc.  Although this may be
true, in the absence of a robust theory as to exactly what feature of
the observed images constitutes \emph{the} bow shock, such variations
nevertheless serve to limit the precision with which the bow shock
shape can be measured.  We therefore conclude that conservative
estimates of \(20\%\) precision for \(\Pi'\) and \(10\%\) precision for
\(\Lambda'\) are appropriate when analyzing observations of a similar or
better quality\footnote{%
  Since the uncertainties are systematic and due to unavoidably
  subjective decisions, it is unlikely that better quality
  observations would improve the situation, although poorer quality
  observations could make things worse.  } %
to those presented in Figure~\ref{fig:000-400-fit}.  This will be an
important limitation when comparing the statistics of the shapes of
different bow shock populations, as we will present in a following
paper.

@@

From a casual inspection of Figure~\ref{fig:000-400-fit}, it is
apparent that the shapes of the two M42 arcs are closely similar, and
this is confirmed by the numbers in Table~\ref{tab:m42-fit}. Both
000-400 and 069-601 are consistent with
\((\Pi', \Lambda') \approx (3.0, 2.5)\), and if we take the absolute minimum over
all the different tracings and reasonable variations in the
\(\Delta\theta\) fit parameter, we find firm lower limits of
\((\Pi', \Lambda') > (2.1, 2.1)\).  In the rest of this section

If we compare th
